Project Uccle

### 2020-06-09 project.Rmd
cleanup some labels

```{r test_train split ts, include=FALSE}
seis.h.start <- as_datetime('2018-10-29T00:00:00')
seis.h.end <- as_datetime('2020-03-02T00:00:00') - seconds(1)
seasonality.period <- 24
seasonality.xlab <- "Days"
seasonality.aggregate <- function(ds) na.aggregate(ds, function(x) floor(x/14))
seasonality.period <- 168
seasonality.xlab <- "Weeks"
seasonality.aggregate <- function(ds) na.aggregate(ds, floor)
seis.h.ts <- build_ts(seis.h, periods = c(seasonality.period), start = seis.h.start, end = seis.h.end, force_ms = T)

@@

# Analysis
```{r whole data plot}
month.starts <- seq.POSIXt(from=floor_date(seis.h.start, 'month'), to=ceiling_date(seis.h.end, 'month'), by = "1 month")
hours.from.start <- as.numeric(month.starts-seis.h.start)*24+168
autoplot(seis.h.ts, type="l") +
  scale_x_continuous(breaks=hours.from.start/168, labels=format(month.starts, "%m-%y")) +
  ylab("mean hourly movement (nm)") + xlab(NULL) + labs(title = "Training set", caption = "Data in original scale")
week.starts <- seq.POSIXt(from=floor_date(seis.h.start, 'week'), to=ceiling_date(seis.h.end, 'week'), by = "1 week")
hours.from.start <- as.numeric(week.starts-seis.h.start)*24+168
autoplot(seis.h.ts, type="l") +
  scale_x_continuous(breaks=hours.from.start/168, labels=format(week.starts, "%d-%m-%y"), limits = c(11,15)-3/24) +
  scale_y_continuous(limits = c(min(seis.h.ts[(10*168):(16*168)]), max(seis.h.ts[(10*168):(16*168)]))) +
  ylab("mean hourly movement (nm)") + xlab(NULL) + labs(title = "Training set", subtitle = "4-weeks zoom", caption = "Data in original scale")
dec.addi <- decompose(seasonality.aggregate(seis.h.ts))
autoplot(dec.addi) + labs(title="Decomposition of additive time series", subtitle = paste0("Seasonality ", seasonality.period)) + xlab("Weeks")
```

@@

autoplot(seis.h.train, type="l") +
  scale_x_continuous(breaks=hours.from.train.start/168, labels=format(month.starts, "%m-%y")) +
  ylab("mean hourly movement (nm)") + xlab(NULL) + ggtitle("Training set") + labs(caption = "Data in original scale")
gghistogram(seis.h.train, add.normal = T) + xlab("mean hourly movement (nm)") + labs(caption = "Data in original scale")
gg_qqplot(seis.h.train) + 
  labs(title="Q-Q plot for training dataset") + ylab("Sample quantiles") + labs(caption = "Data in original scale")

autoplot(log(seis.h.train), type="l") +
  scale_x_continuous(breaks=hours.from.train.start/168, labels=format(month.starts, "%m-%y")) +
  ylab("mean hourly movement (nm)") + xlab(NULL) + ggtitle("Training set") + labs(caption = "Data in log-scale")
gghistogram(log(seis.h.train), add.normal = T) + xlab("mean hourly movement (nm)") + labs(caption = "Data in log-scale")
gg_qqplot(log(seis.h.train)) + 
  labs(title="Q-Q plot for training dataset") + ylab("Sample quantiles") + labs(caption = "Data in log-scale")

train.bc.lambda <- BoxCox.lambda(seis.h.train)
train.bc <- BoxCox(seis.h.train, train.bc.lambda)
autoplot(train.bc, type="l") +
  scale_x_continuous(breaks=hours.from.train.start/168, labels=format(month.starts, "%m-%y")) +
  ylab("mean hourly movement (nm)") + xlab(NULL) + ggtitle("Training set") + labs(caption = paste0("Data Box-Cox transformed with lambda = ", train.bc.lambda))
gghistogram(train.bc, add.normal = T) + xlab("mean hourly movement (nm)") + labs(caption = paste0("Data Box-Cox transformed with lambda = ", train.bc.lambda))
gg_qqplot(train.bc) + 
  labs(title="Q-Q plot for training dataset") + ylab("Sample quantiles") + labs(caption = paste0("Data Box-Cox transformed with lambda = ", train.bc.lambda))
```

@@

```{r show_overlap_and_diff, include=FALSE}
show_overlap_and_diff <- function(base, compare, base.desc, compare.desc, xlab, overlap.ylab, diff.title, diff.ylab, diff.ylab.sec, diff.ylab.sec.accuracy=.1) {
  overlap_plot <-
    autoplot(compare, xlab=xlab, ylab=overlap.ylab) +
      geom_line(aes(y=base, col="red"), show.legend = F) +
      labs(title=paste0(base.desc, " vs ", compare.desc))
  diff <- compare-base

@@

plots <- show_overlap_and_diff(
  seis.h.train, ts, xlab=seasonality.xlab,
  base.desc = "original series",
  compare.desc = "reconstructed serie (manual)",
  overlap.ylab = "Mean hourly movement (nm)",
  diff.title = "Difference between ts",
  diff.ylab = "nm", diff.ylab.sec="% over ts span",
  diff.ylab.sec.accuracy = .01
)
plot_grid(plots[[1]], plots[[2]], nrow = 2)

plots <- show_overlap_and_diff(
  seis.h.train, dec.addi$trend+dec.addi$seasonal+dec.addi$random, xlab=seasonality.xlab,
  base.desc = "original series",
  compare.desc = "reconstructed serie (decompose additive)",
  overlap.ylab = "Mean hourly movement (nm)",
  diff.title = "Difference between ts",
  diff.ylab = "nm", diff.ylab.sec="% over ts span",
  diff.ylab.sec.accuracy = .01
)
plot_grid(plots[[1]], plots[[2]], nrow = 2)

@@

plots <- show_overlap_and_diff(
  seasonbase.168$figure, season.168$figure + rep(season.24$figure, 7), xlab="Hours",
  base.desc = "168 from ds",
  compare.desc = "168+24 from ds",
  overlap.ylab = "Mean hourly movement (nm)",
  diff.title = "Difference between 168",
  diff.ylab = "nm", diff.ylab.sec="% over season span",
  diff.ylab.sec.accuracy = .01
)
plot_grid(plots[[1]], plots[[2]], nrow = 2)

>>>>

```{r test_train split ts, include=FALSE}
data.lab <- "Hourly mean (nm)"

seis.h.start <- as_datetime('2018-10-29T00:00:00')
seis.h.end <- as_datetime('2020-03-02T00:00:00') - seconds(1)
seasonality.period <- 24
seasonality.xlab <- "Days"
seasonality.aggregate <- function(ds) na.aggregate(ds, function(x) floor(x/14))
seasonality.period <- 168
seasonality.xlab <- "Weeks"
seasonality.aggregate <- function(ds) na.aggregate(ds, floor)
seis.h.ts <- build_ts(seis.h, periods = c(seasonality.period), start = seis.h.start, end = seis.h.end, force_ms = T)

@@

# Analysis
```{r whole data plot}
month.starts <- seq.POSIXt(from=floor_date(seis.h.start, 'month'), to=ceiling_date(seis.h.end, 'month'), by = "1 month")
hours.from.start <- as.numeric(month.starts-seis.h.start)*24+168
autoplot(seis.h.ts, type="l") +
  scale_x_continuous(breaks=hours.from.start/168, labels=format(month.starts, "%m-%y")) +
  ylab(data.lab) + xlab(NULL) + labs(title = "Training set", caption = "Data in original scale")
week.starts <- seq.POSIXt(from=floor_date(seis.h.start, 'week'), to=ceiling_date(seis.h.end, 'week'), by = "1 week")
hours.from.start <- as.numeric(week.starts-seis.h.start)*24+168
autoplot(seis.h.ts, type="l") +
  scale_x_continuous(breaks=hours.from.start/168, labels=format(week.starts, "%d-%m-%y"), limits = c(11,15)-3/24) +
  scale_y_continuous(limits = c(min(seis.h.ts[(10*168):(16*168)]), max(seis.h.ts[(10*168):(16*168)]))) +
  ylab(data.lab) + xlab(NULL) + labs(title = "Training set", subtitle = "4-weeks zoom", caption = "Data in original scale")
dec.addi <- decompose(seasonality.aggregate(seis.h.ts))
autoplot(dec.addi) + labs(title="Decomposition of additive time series", subtitle = paste0("Seasonality ", seasonality.period)) + xlab("Weeks")
```

@@

autoplot(seis.h.train, type="l") +
  scale_x_continuous(breaks=hours.from.train.start/168, labels=format(month.starts, "%m-%y")) +
  ylab(data.lab) + xlab(NULL) + ggtitle("Training set") + labs(caption = "Data in original scale")
gghistogram(seis.h.train, add.normal = T) + xlab(data.lab) + labs(caption = "Data in original scale")
gg_qqplot(seis.h.train) + 
  labs(title="Q-Q plot for training dataset") + ylab("Sample quantiles") + labs(caption = "Data in original scale")

autoplot(log(seis.h.train), type="l") +
  scale_x_continuous(breaks=hours.from.train.start/168, labels=format(month.starts, "%m-%y")) +
  ylab(data.lab) + xlab(NULL) + ggtitle("Training set") + labs(caption = "Data in log-scale")
gghistogram(log(seis.h.train), add.normal = T) + xlab(data.lab) + labs(caption = "Data in log-scale")
gg_qqplot(log(seis.h.train)) + 
  labs(title="Q-Q plot for training dataset") + ylab("Sample quantiles") + labs(caption = "Data in log-scale")

train.bc.lambda <- BoxCox.lambda(seis.h.train)
train.bc <- BoxCox(seis.h.train, train.bc.lambda)
autoplot(train.bc, type="l") +
  scale_x_continuous(breaks=hours.from.train.start/168, labels=format(month.starts, "%m-%y")) +
  ylab(data.lab) + xlab(NULL) + ggtitle("Training set") + labs(caption = paste0("Data Box-Cox transformed with lambda = ", train.bc.lambda))
gghistogram(train.bc, add.normal = T) + xlab(data.lab) + labs(caption = paste0("Data Box-Cox transformed with lambda = ", train.bc.lambda))
gg_qqplot(train.bc) + 
  labs(title="Q-Q plot for training dataset") + ylab("Sample quantiles") + labs(caption = paste0("Data Box-Cox transformed with lambda = ", train.bc.lambda))
```

@@

```{r show_overlap_and_diff, include=FALSE}
show_overlap_and_diff <- function(base, compare, base.desc, compare.desc, xlab, overlap.ylab, diff.title, diff.ylab, diff.ylab.sec, diff.ylab.sec.accuracy=.1) {
  overlap_plot <-
    autoplot(compare, xlab=xlab, ylab=overlap.ylab) +
      geom_line(aes(y=base, col="red"), show.legend = F) +
      labs(title=NULL, subtitle=paste0(base.desc, " vs ", compare.desc))
  diff <- compare-base

@@

plots <- show_overlap_and_diff(
  seis.h.train, ts, xlab=seasonality.xlab,
  base.desc = "original series",
  compare.desc = "reconstructed serie (manual)",
  overlap.ylab = data.lab,
  diff.title = "Difference between ts",
  diff.ylab = "nm", diff.ylab.sec="% over ts span",
  diff.ylab.sec.accuracy = .01
)
plot_grid(plots[[1]], plots[[2]], nrow = 2)

plots <- show_overlap_and_diff(
  seis.h.train, dec.addi$trend+dec.addi$seasonal+dec.addi$random, xlab=seasonality.xlab,
  base.desc = "original series",
  compare.desc = "reconstructed serie (decompose additive)",
  overlap.ylab = data.lab,
  diff.title = "Difference between ts",
  diff.ylab = "nm", diff.ylab.sec="% over ts span",
  diff.ylab.sec.accuracy = .01
)
plot_grid(plots[[1]], plots[[2]], nrow = 2)

@@

plots <- show_overlap_and_diff(
  seasonbase.168$figure, season.168$figure + rep(season.24$figure, 7), xlab="Hours",
  base.desc = "168 from ds",
  compare.desc = "168+24 from ds",
  overlap.ylab = data.lab,
  diff.title = "Difference between 168",
  diff.ylab = "nm", diff.ylab.sec="% over season span",
  diff.ylab.sec.accuracy = .01
)
plot_grid(plots[[1]], plots[[2]], nrow = 2)

### 2020-06-09 project.after.Rmd
cleanup some labels

final.training <- build_ts(seis.h, periods = c(seasonality.period), start = seis.train.start, end = seis.test.end, force_ms = T)
final.testing <- build_ts(seis.h, periods = c(seasonality.period), start = seis.train.start, end = seis.test.final.end, force_ms = T)
final.testing <- window(final.testing, start = c(end(final.training)[1] + 1, 1))
if (!is.null(chosen.lambda)) {
  cat(chosen.lambda, BoxCox.lambda(final.training), chosen.lambda == BoxCox.lambda(final.training), "\n")
}

fit.name <- paste0("fit", paste0(chosen.model, collapse = ""))
forecast.name <- paste0("forecast", paste0(chosen.model, collapse = ""))
cat("SARIMA(", paste0(chosen.model[1:3], collapse = ","), ")(", paste0(chosen.model[4:6], collapse = ","), ")[", frequency(final.training), "]", sep = "")
if (!exists("final.model")) {
  cat(" fitting...")
  final.model <- Arima(final.training, chosen.model[1:3], chosen.model[4:6], lambda=chosen.lambda)
  cat("DONE")
}
if (!exists("final.forecast")) {
  cat(" forecasting...")
  final.forecast <- forecast(final.model, h=168*8, lambda=chosen.lambda)
  cat("DONE")
}
cat("\n")
plotting.model <- final.model
plotting.forecast <- final.forecast
print(plotting.model)
print(autoplot(plotting.model) + labs(subtitle = plotting.forecast$method))
checkresiduals(plotting.model)
residuals.acf <- autoplot(acf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=168*4)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method))
residuals.pacf <- autoplot(pacf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=168*4)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method))
print(plot_grid(residuals.acf, residuals.pacf, nrow=2))
print(plot_grid(
  autoplot(acf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=24)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method)),
  residuals.acf,
  autoplot(pacf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=24)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method)),
  residuals.pacf,
  nrow = 2
))
print(plot_forecast(plotting.forecast) + autolayer(final.testing, series="Original") + ylab("Mean hourly movement (nm)") + xlab("Weeks") + geom_vline(aes(xintercept=as.integer(as_datetime('2020-03-14T00:00:00') - seis.train.start)/7+1), linetype=2))
plots <- show_overlap_and_diff(
  final.training, plotting.forecast$fitted, xlab=seasonality.xlab,
  base.desc = "training set",
  compare.desc = paste0("refit with ", plotting.forecast$method),
  overlap.ylab = "Mean hourly movement (nm)",
  diff.title = "Difference between ts",
  diff.ylab = "nm", diff.ylab.sec="%",
  diff.ylab.sec.accuracy = .01
)
print(plot_grid(plots[[1]], plots[[2]], nrow = 2))

cat("Test set inside the CI\n")
cat("80% CI \t ", print_dec(mean(plotting.forecast$lower[,1] < final.testing & final.testing < plotting.forecast$upper[,1], na.rm = T)*100), "%\n")
cat("95% CI \t ", print_dec(mean(plotting.forecast$lower[,2] < final.testing & final.testing < plotting.forecast$upper[,2], na.rm = T)*100), "%\n")

plots <- show_overlap_and_diff(
  final.testing, plotting.forecast$mean, xlab=seasonality.xlab,
  base.desc = "test set",
  compare.desc = paste0("forecast with ", plotting.forecast$method),
  overlap.ylab = "Mean hourly movement (nm)",
  diff.title = "Difference between ts",
  diff.ylab = "nm", diff.ylab.sec="%",
  diff.ylab.sec.accuracy = .01
)
print(plot_grid(plots[[1]] + geom_vline(aes(xintercept=as.integer(as_datetime('2020-03-14T00:00:00') - seis.train.start)/7+1), linetype=2),
                plots[[2]] + geom_vline(aes(xintercept=as.integer(as_datetime('2020-03-14T00:00:00') - seis.train.start)/7+1), linetype=2),
                nrow = 2
                ))

print(accuracy(plotting.forecast, final.testing))
# qqPlot(plotting.model$residuals, main = paste0("Q-Q plot for ", plotting.forecast$method), xlab = "residuals")
print(gg_qqplot(plotting.model$residuals) + 
    labs(title=paste0("Q-Q plot for ", plotting.forecast$method, " residuals")) + ylab("Residuals quantiles")
)

@@

autoplot(ts(seasonbase.after.lockdown.168.df$figure, frequency=1)) + ylab("") + xlab("Hours") + scale_x_continuous() +
  geom_ribbon(aes(ymin = (seasonbase.after.lockdown.168.df$figure - seasonbase.after.lockdown.168.df$sd), ymax = (seasonbase.after.lockdown.168.df$figure + seasonbase.after.lockdown.168.df$sd)), fill = "mediumpurple1", alpha=0.5) +
  geom_line(aes(col="After lockdown")) +
  geom_ribbon(aes(ymin = seasonbase.before.lockdown.168.df$figure - seasonbase.before.lockdown.168.df$sd, ymax = seasonbase.before.lockdown.168.df$figure + seasonbase.before.lockdown.168.df$sd), fill = "lightcoral", alpha=0.5) +
  geom_line(aes(y=seasonbase.before.lockdown.168.df$figure, col="Before lockdown")) +
  scale_colour_manual("", values=c("purple", "red"), breaks=c("After lockdown", "Before lockdown"))
```
```{r seasonalities/seasonplot-mean-sd}
ggplot(data=seasonbase.before.lockdown.168.df) +
  geom_line(aes(Hour, figure - sd, col=Weekday), alpha=.1) +
  geom_line(aes(Hour, figure + sd, col=Weekday), alpha=.1) +
  geom_ribbon(aes(Hour, ymin = figure - sd, ymax = figure + sd, fill = Weekday), alpha=0.1, show.legend=F) +
  geom_line(aes(Hour, figure, col=Weekday)) +
  ylab("Mean hourly movement (nm)") +
  labs(title="Seasonal plot: before lockdown") +
  scale_color_manual(values = rainbow(7), breaks=weekdays, aesthetics = c("colour", "fill"))

ggplot(data=seasonbase.after.lockdown.168.df) +
  geom_line(aes(Hour, figure - sd, col=Weekday), alpha=.1) +
  geom_line(aes(Hour, figure + sd, col=Weekday), alpha=.1) +
  geom_ribbon(aes(Hour, ymin = figure - sd, ymax = figure + sd, fill = Weekday), alpha=0.1, show.legend=F) +
  geom_line(aes(Hour, figure, col=Weekday)) +
  ylab("Mean hourly movement (nm)") +
  labs(title="Seasonal plot: after lockdown") +
  scale_color_manual(values = rainbow(7), breaks=weekdays, aesthetics = c("colour", "fill"))
```

>>>>

final.training <- build_ts(seis.h, periods = c(seasonality.period), start = seis.train.start, end = seis.test.end, force_ms = T)
final.testing <- build_ts(seis.h, periods = c(seasonality.period), start = seis.train.start, end = seis.test.final.end, force_ms = T)
final.testing <- window(final.testing, start = c(end(seis.h.test)[1] + 1, 1))
if (!is.null(chosen.lambda)) {
  cat(chosen.lambda, BoxCox.lambda(final.training), chosen.lambda == BoxCox.lambda(final.training), "\n")
}

fit.name <- paste0("fit", paste0(chosen.model, collapse = ""))
forecast.name <- paste0("forecast", paste0(chosen.model, collapse = ""))
cat("SARIMA(", paste0(chosen.model[1:3], collapse = ","), ")(", paste0(chosen.model[4:6], collapse = ","), ")[", frequency(final.training), "]", sep = "")
if (!exists("full.forecast")) {
  cat(" forecasting...")
  full.forecast <- forecast(models[[fit.name]], h=168*26, lambda = chosen.lambda)
  cat("DONE")
}
cat("\n")
plotting.model <- models[[fit.name]]
plotting.forecast <- full.forecast
print(plotting.model)
print(autoplot(plotting.model) + labs(subtitle = plotting.forecast$method))
checkresiduals(plotting.model)
residuals.acf <- autoplot(acf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=168*4)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method))
residuals.pacf <- autoplot(pacf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=168*4)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method))
print(plot_grid(residuals.acf, residuals.pacf, nrow=2))
print(plot_grid(
  autoplot(acf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=24)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method)),
  residuals.acf,
  autoplot(pacf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=24)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method)),
  residuals.pacf,
  nrow = 2
))
lockdown.x <- as.integer(as_datetime('2020-03-14T00:00:00') - seis.train.start)/7+1
print(
  plot_forecast(plotting.forecast)
      + autolayer(ts_c(`Before March '20`=seis.h.test, `From March '20`=final.testing))
      + ylab(data.lab)
      + xlab("Weeks")
      + geom_vline(aes(xintercept=lockdown.x), linetype=2)
)
plots <- show_overlap_and_diff(
  seis.h.train, plotting.forecast$fitted, xlab=seasonality.xlab,
  base.desc = "training set",
  compare.desc = paste0("refit with ", plotting.forecast$method),
  overlap.ylab = data.lab,
  diff.title = "Difference between ts",
  diff.ylab = "nm", diff.ylab.sec="%",
  diff.ylab.sec.accuracy = .01
)
print(plot_grid(plots[[1]], plots[[2]], nrow = 2))
seis.h.test.len <- length(seis.h.test)
final.testing.len <- length(final.testing)
full.forecast.len <- seis.h.test.len + final.testing.len
full.forecast.before.ids <- 1:seis.h.test.len
full.forecast.after.ids <- (seis.h.test.len+1):full.forecast.len
cat("Test set inside the CI\n")
cat("CI   ", "Overall ", "Before  ", "After  \n")
cat("80 % ",
    print_dec(mean(plotting.forecast$lower[,1] < c(seis.h.test, final.testing) & c(seis.h.test, final.testing) < plotting.forecast$upper[,1], na.rm = T)*100),
    "% ",
    print_dec(mean(plotting.forecast$lower[full.forecast.before.ids,1] < seis.h.test & seis.h.test < plotting.forecast$upper[full.forecast.before.ids,1], na.rm = T)*100),
    "% ",
    print_dec(mean(plotting.forecast$lower[full.forecast.after.ids,1] < final.testing & final.testing < plotting.forecast$upper[full.forecast.after.ids,1], na.rm = T)*100),
    "%\n")
cat("95 % ",
    print_dec(mean(plotting.forecast$lower[,2] < c(seis.h.test, final.testing) & c(seis.h.test, final.testing) < plotting.forecast$upper[,2], na.rm = T)*100),
    "% ",
    print_dec(mean(plotting.forecast$lower[full.forecast.before.ids,2] < seis.h.test & seis.h.test < plotting.forecast$upper[full.forecast.before.ids,2], na.rm = T)*100),
    "% ",
    print_dec(mean(plotting.forecast$lower[full.forecast.after.ids,2] < final.testing & final.testing < plotting.forecast$upper[full.forecast.after.ids,2], na.rm = T)*100),
    "%\n")

plots <- show_overlap_and_diff(
  c(seis.h.test, final.testing), plotting.forecast$mean, xlab=seasonality.xlab,
  base.desc = "test set",
  compare.desc = paste0("forecast with ", plotting.forecast$method),
  overlap.ylab = data.lab,
  diff.title = NULL,
  diff.ylab = "nm", diff.ylab.sec="%",
  diff.ylab.sec.accuracy = .01
)
print(plot_grid(plots[[1]] + geom_vline(aes(xintercept=lockdown.x), linetype=2), plots[[2]] + geom_vline(aes(xintercept=lockdown.x), linetype=2), nrow = 2))

plots <- show_overlap_and_diff(
  seis.h.test, window(plotting.forecast$mean, start=c(53,1), end=c(70,168)), xlab=seasonality.xlab,
  base.desc = "test set before lockdown",
  compare.desc = paste0("forecast with ", plotting.forecast$method),
  overlap.ylab = data.lab,
  diff.title = NULL,
  diff.ylab = "nm", diff.ylab.sec="%",
  diff.ylab.sec.accuracy = .01
)
print(plot_grid(plots[[1]], plots[[2]], nrow = 2))

plots <- show_overlap_and_diff(
  final.testing, window(plotting.forecast$mean, start=c(71,1), end=c(78,168)), xlab=seasonality.xlab,
  base.desc = "test set during lockdown",
  compare.desc = paste0("forecast with ", plotting.forecast$method),
  overlap.ylab = data.lab,
  diff.title = NULL,
  diff.ylab = "nm", diff.ylab.sec="%",
  diff.ylab.sec.accuracy = .01
)
print(plot_grid(plots[[1]] + geom_vline(aes(xintercept=lockdown.x), linetype=2), plots[[2]] + geom_vline(aes(xintercept=lockdown.x), linetype=2), nrow = 2))

print(accuracy(plotting.forecast, c(seis.h.test, final.testing)))
# qqPlot(plotting.model$residuals, main = paste0("Q-Q plot for ", plotting.forecast$method), xlab = "residuals")
print(gg_qqplot(plotting.model$residuals) + 
    labs(title=paste0("Q-Q plot for ", plotting.forecast$method, " residuals")) + ylab("Residuals quantiles")
)

@@

autoplot(ts(seasonbase.after.lockdown.168.df$figure, frequency=1)) + ylab("") + xlab("Hours") + scale_x_continuous() +
  geom_ribbon(aes(ymin = (seasonbase.after.lockdown.168.df$figure - seasonbase.after.lockdown.168.df$sd), ymax = (seasonbase.after.lockdown.168.df$figure + seasonbase.after.lockdown.168.df$sd)), fill = "mediumpurple1", alpha=0.5) +
  geom_line(aes(col="After lockdown")) +
  geom_ribbon(aes(ymin = seasonbase.before.lockdown.168.df$figure - seasonbase.before.lockdown.168.df$sd, ymax = seasonbase.before.lockdown.168.df$figure + seasonbase.before.lockdown.168.df$sd), fill = "lightcoral", alpha=0.5) +
  geom_line(aes(y=seasonbase.before.lockdown.168.df$figure, col="Before lockdown")) +
  scale_colour_manual("", values=c("purple", "red"), breaks=c("After lockdown", "Before lockdown"))
```
```{r seasonalities/seasonplot-mean-sd}
ggplot(data=seasonbase.before.lockdown.168.df) +
  geom_line(aes(Hour, figure - sd, col=Weekday), alpha=.1) +
  geom_line(aes(Hour, figure + sd, col=Weekday), alpha=.1) +
  geom_ribbon(aes(Hour, ymin = figure - sd, ymax = figure + sd, fill = Weekday), alpha=0.1, show.legend=F) +
  geom_line(aes(Hour, figure, col=Weekday)) +
  ylab(data.lab) +
  labs(title="Seasonal plot: before lockdown") +
  scale_color_manual(values = rainbow(7), breaks=weekdays, aesthetics = c("colour", "fill"))

ggplot(data=seasonbase.after.lockdown.168.df) +
  geom_line(aes(Hour, figure - sd, col=Weekday), alpha=.1) +
  geom_line(aes(Hour, figure + sd, col=Weekday), alpha=.1) +
  geom_ribbon(aes(Hour, ymin = figure - sd, ymax = figure + sd, fill = Weekday), alpha=0.1, show.legend=F) +
  geom_line(aes(Hour, figure, col=Weekday)) +
  ylab(data.lab) +
  labs(title="Seasonal plot: after lockdown") +
  scale_color_manual(values = rainbow(7), breaks=weekdays, aesthetics = c("colour", "fill"))
```
